---
title: 'Documentation: Check_TrainingData.R'
author: "Fabian Schumacher, Henning Sander, Frederik Bruch, Thalis Goldschmidt, Jakob Danel"
date: "30 1 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# checkTrainingData(path)
This function is validating the incoming training data for their usability to train the model.
The function returning status codes which indicating if they data are valid, and if not why their are not valid:
**paramters:** \
**path:** The path to the file where the training data are stored. \
**return:** An status code: \
**0** - The training data are valid \
**1** - The training data have no column with the value "Label" \
**2** - Some features do not contain Label values \
**3** - The geometry of the object is not Polygon
```{r checkTrainingData}
checkTrainingData <- function(path) {
 library(sf)
 trainingData <- read_sf(path)
  
 
 #Checking the geometry
 geometry <- trainingData$geom
 if(is.null(geometry)){
   geometry <- trainingData$geometry
 }
 if(class(geometry)[1] != "sfc_POLYGON"){
   #error Code 3: The training data have no column with the value "Label"
   return(3)
 }
 
 
 
 #Checking the Label
 labels <- trainingData$Label
 if(is.null(labels)){
   # Errir code 1: The training data have no column with the value "Label"
   return(1)
 }
 has_NA <- any(is.na(labels))
 if(has_NA){
   # Error code 2: The geometry of the object is not Polygon
   return(2)
 }
 return(0) #Training Data are valid
}
```
