---
title: "Documentation GetSatelliteImages.R"
author: "Jakob Danel, Thalis Goldschmidt"
date: "25-01-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Functions

### getUTMZone(longitude)
A function that returns a UTM zone to a given longitude. \
**parameters:** \
**longitude** (Float) of a coordinate in WGS84 \
**returns:** (Number) The Number of the UTM zone from the given longitude
```{r getUTMZone}
getUTMZone <- function (longitude){
  return( (floor((longitude + 180)/6) %% 60) + 1)
}
```
### epsgCodeFromUTMzone(utmZone)
Function that gets the EPSG code from a UTM zone.
All EPSG codes to be returned are in UTM coordinates of WGS84. \
**parameters:** \
**utmZone** (Integer) The zone number \
**returns:** (String) The EPSG Code of the given utmZone
```{r epsgCodeFromUTMzone}
epsgCodeFromUTMzone <- function(utmZone){
  if(utmZone < 10){
    x <- toString(utmZone)
    string = paste("0",x,sep = "")
    
  }else{
    string = toString(utmZone)
  }
  return(paste("EPSG:326",string, sep=""))
}
```
### getEPSG(longitude)
Function that returns the EPSG code of an CRS depending on the longitude.
All EPSG codes to be returned are in UTM coordinates of WGS84.\
**parameters:** \
**longitude** (Float) of a coordinate in WGS84 \
**returns:** (String) The EPSG code of the given longitude
```{r getEPSG}
getEPSG <- function(longitude){
  zone <- getUTMZone(longitude)
  epsg <- epsgCodeFromUTMzone(zone)
  return(epsg)
}
```
### bboxToWGS84(bbox)
Function to transform a bbox of any CRS to a bbox with a WGS84 CRS. \
**parameters:** \
**bbox** of the area of interest \
**returns:** (bbox) The bbox in WGS84 coordinate system
```{r bboxToWGS84}
bboxToWGS84 <- function(bbox){
  library(sf)
  st_as_sfc(bbox) %>%
    st_transform("EPSG:4326") %>%
    st_bbox() -> bbox_WGS84
  return(bbox_WGS84)
}
```

### getBBoxFromAOI(bottomLeftX,bottomLeftY,topRightX,topRightY)
Function that creates a bbox from two coordinates (bottom left and top right coordinates). \
**parameters:** \
**bottomLeftX** (Float) \
**bottomLeftY** (Float)\
**topRightX** (Float) \
**topRightY** (Float) \
**returns:** (bbox) An bbox object from the given bounding box coordinates
```{r getBBoxFromAOI}
getBBoxFromAOI <- function(bottomLeftX,bottomLeftY,topRightX,topRightY) {
  library(rgeos)
  bbox <- rgeos::bbox2SP(n = topRightY, s = bottomLeftY, w = bottomLeftX, e = topRightX,
                         proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
  return (bbox)
}
```
### transformBBOXcrsToUTM(bboxWGS84)
Function that transforms a bbox with a WGS84 CRS to a bbox with the same CRS used in the cube view function.\
**parameters:** \
**bboxWGS84** bbox of the area of interest in WGS84 \
**returns:** bbox in the reference system with the correct UTM zone
```{r transformBBOXcrsToUTM}
transformBBOXcrsToUTM <- function(bboxWGS84){
  library(rgdal)
  if (!is.null(bboxWGS84@bbox[1,1])){
    crs = getEPSG(bboxWGS84@bbox[1,1])
  }
  else{
    crs = getEPSG(xmin(extent(bboxWGS84)))
  }
  bbox <- spTransform(bboxWGS84, CRS(crs))
  return (bbox)
}
```

### transformTrainingDataToCRSFromCube(trainingData)
Function that transforms the training data to the same CRS used in the cube view function.\
**parameters:** \
**trainingData** \
**returns:** The trainingData transformed into the UTM zone of the cube view
```{r transformTrainingDataToCRSFromCube}
transformTrainingDataToCRSFromCube <- function(trainingData) {
  bbox = st_bbox(trainingData)
  bboxWGS84 = bboxToWGS84(bbox)
  lon = bboxWGS84["xmin"]
  crs = getEPSG(lon)
  trainingDataInCRSFromCube <- st_transform(trainingData, crs)
  return (trainingDataInCRSFromCube)
}
```
### numberOfDaysFromPeriod(datetime)
Function that returns the number of days that are within a date period (last day excluded).\
**parameters:** \ 
**datetime** (String): "YYYY-MM-DD/YYYY-MM-DD" \
**returns:** (Number) The number of days in this period
```{r numberOfDaysFromPeriod}
numberOfDaysFromPeriod <- function(datetime) {
  date1 <- substr(datetime,12,21)
  date1 <- gsub(pattern = "-", replacement = "/",date1, fixed = TRUE)
  date2 <- substr(datetime,0,10)
  date2 <- gsub(pattern = "-", replacement = "/",date2, fixed = TRUE)
  survey <- data.frame(date=date1, tx_start=date2)
  survey$date_diff <- as.Date(as.character(survey$date), format="%Y/%m/%d")-
    as.Date(as.character(survey$tx_start), format="%Y/%m/%d")
  survey$date_diff<-as.numeric(survey$date_diff)
  return(survey$date_diff)
}
```
### stacRequest(bbox, datetime, limit)
Function that returns useable satellite images from the stac catalogue. \
**parameters:** \
**bbox** of area of interest in any CRS \
**datetime** (String): (example: "2021-06-01/2021-06-30") \
**limit** (Integer) -> maximum count of found images from stac to be used
**returns:** The stac image collection of the parameter matching images
```{r stacRequest}
stacRequest <- function(bbox, datetime, limit) {
  library(rstac)
  s = stac("https://earth-search.aws.element84.com/v0")
  bbox = bboxToWGS84(bbox)
  items = s %>%
    stac_search(collections = "sentinel-s2-l2a-cogs",
                bbox = c(bbox["xmin"],bbox["ymin"],
                         bbox["xmax"],bbox["ymax"]), 
                datetime = datetime,
                limit = limit) %>%
    post_request()
  return(items)
}
```

### createImageCollection(desiredBands, cloudCoverageInPercentage, items)
Function that creates an image collection. \
**parameters:** \
**desiredBands** (vector of Strings): c("B01", "B02", "B03", "SCL") (SCL-BAND MUST BE INCLUDED) \
**cloudCoverageInPercentage** (Float) \
**items** found by the stac request \
**returns** 3 if after the cloudFilter no Images are left, else the imageCollection
```{r createImageCollection}
createImageCollection <- function(desiredBands, cloudCoverageInPercentage, items){
  library(gdalcubes)
  s2_collection <- tryCatch(
    {
      stac_image_collection(items$features, asset_names = desiredBands, property_filter = function(x) {x[["eo:cloud_cover"]] <= cloudCoverageInPercentage})
    },
    error=function(cond) {
      return(3)
    },
    finally={
    }
    )
  return(s2_collection)
}
```
### createCubeView(bboxUTM, resolution, datetime)
Function that creates the view of a cube. \
**parameters:** \
**bbox** of area of interest in UTM coordinates \
**resolution** in meters (Integer): (options: 10/20/60/100/200/400) \
**datetime** (String): (example: "2021-06-01/2021-06-30") \
**returns** The cube view of the given data
```{r createCubeView}
createCubeView <- function(bboxUTM, resolution, datetime){
  bboxWGS84 = bboxToWGS84(bboxUTM)
  bboxUTM = st_bbox(bboxUTM) # goal: access the bbox in the cube_view function everytime in the same way like (bboxUTM["xmin"])
  lon = bboxWGS84["xmin"]
  crs = getEPSG(lon)
  days = numberOfDaysFromPeriod(datetime) +1
  daysString = paste("P",days,"D",sep = "")
  v.bbox.overview = cube_view(srs= crs,  dx=resolution, dy=resolution, dt= daysString, 
                              aggregation="median", resampling = "average",
                              extent=list(t0 = substr(datetime,0,10), t1 = substr(datetime,12,21),
                              left=bboxUTM["xmin"] - 1000, right=bboxUTM["xmax"] + 1000,
                              top=bboxUTM["ymax"] + 1000, bottom=bboxUTM["ymin"] - 1000))
  return (v.bbox.overview)
}
```
### createTifFileFromTrainingDat(imageCollection, cubeView, trainingData)
Function that creates the needed satellite image from the training data as a tif file. \
**parameters:** \
**image collection** (from createImageCollection function) \
**cube view** (from createCubeView function) \
**training data** \
**returns** (void)
```{r createTifFileFromTrainingData}
createTifFileFromTrainingData <- function(imageCollection, cubeView, trainingData){
  # Set mask for further cloud filtering
  S2.mask = image_mask("SCL", values = c(3,8,9))
  # Create raster cube and filter images by the geometry of the training data
  if (!is.null(trainingData$geom)){
    sentinel <- raster_cube(imageCollection, cubeView, S2.mask) %>%
      filter_geom(trainingData$geom)
  }
  else if(!is.null(trainingData$geometry)) {
    sentinel <- raster_cube(imageCollection, cubeView, S2.mask) %>%
      filter_geom(trainingData$geometry)
  }
  #print(sentinel)
  write_tif(
    sentinel,
    dir = "./R/processed_sentinel_images",
    prefix = 'trainingData_',
    overviews = FALSE,
    COG = TRUE,
    rsmpl_overview = "nearest",
    creation_options = NULL,
    write_json_descr = FALSE,
    pack = NULL
  )
  files <- list.files(path="./R/processed_sentinel_images/")
  file.rename(paste("./R/processed_sentinel_images/",files[2],sep=""),"./R/processed_sentinel_images/trainingData.tif")
}
```

### generateSatelliteImageFromTrainingData(trainingDataPath, datetime, limit, desiredBands, resolution, cloudCoverageInPercentage)
Function that combines all prior functions to one function. It generates a satellite image as a tif file.\
**parameters:** \
**trainingDataPath:** path to where the training data is stored \
**datetime** (String): (example: "2021-06-01/2021-06-30") \
**resolution** in meters (Integer): (options: 10/20/60/100/200/400) \
**limit** (Integer) -> maximum count of found images from stac to be used \
**desiredBands** (vector of Strings): c("B01", "B02", "B03", "SCL") (SCL-BAND MUST BE INCLUDED) \
**cloudCoverageInPercentage** (Float) \
**returns:** See return codes
```{r generateSatelliteImageFromTrainingData}
generateSatelliteImageFromTrainingData <- function(trainingDataPath, datetime, limit, desiredBands, resolution, cloudCoverageInPercentage) {
  library(sf)
  # Read the path to upload the training data
  trainingData <- read_sf(trainingDataPath)
  # Transform training data to the same CRS we use to create the cube view, so that every geometry alligns to each other
  trainingData <- transformTrainingDataToCRSFromCube(trainingData)
  # Set BBOX to bbox of the shape and crs (UTM) from the training data
  bbox = st_bbox(trainingData)
  # Querying images with rstac
  items = stacRequest(bbox, datetime, limit)
  if (length(items$features) == 0) {
    return(1)
  }
  # print(items)
  # Creating an image collection
  imageCollection =  createImageCollection(desiredBands, cloudCoverageInPercentage, items)
  if (is.numeric(imageCollection)) {
    return(3)
  }
  # print(imageCollection)
  # Creating the cube view
  cubeView = createCubeView(bbox, resolution, datetime)
  # print(cubeView)
  # Parallel computing
  gdalcubes_options(threads = 16)
  # Create tif file
  createTifFileFromTrainingData(imageCollection, cubeView, trainingData)
  return(0)
}
``` 
### createTifFileFromAOI(imageCollection,cubeView)
Function that creates the needed satellite image from the training data as a tif file. \
**parameters:** \
**image collection** (from createImageCollection function) \
**cube view** (from createCubeView function) \
**returns:** (void)
```{r createTifFileFromAOI}
createTifFileFromAOI <- function(imageCollection,cubeView){
  files <- list.files(path="./R/processed_sentinel_images/")
  files
  for (i in 1:length(files)) {
    file.remove(paste("./R/processed_sentinel_images/",files[i],sep=""))
  }
  # Set mask for further cloud filtering
  S2.mask = image_mask("SCL", values = c(3,8,9))
  # Create raster cube
  sentinel <- raster_cube(imageCollection, cubeView, S2.mask) 
  #print(sentinel)
  write_tif(
    sentinel,
    dir = "./R/processed_sentinel_images",
    prefix = "aoi_",
    overviews = FALSE,
    COG = TRUE,
    rsmpl_overview = "nearest", 
    creation_options = NULL,
    write_json_descr = FALSE,
    pack = NULL
  )
  files <- list.files(path="./R/processed_sentinel_images/")
  file.rename(paste("./R/processed_sentinel_images/",files[1],sep=""),"./R/processed_sentinel_images/aoi.tif")

}
```
### generateSatelliteImageFromAOI(bottomLeftX,bottomLeftY,topRightX,topRightY,datetime,limit,desiredBands,resolution,cloudCoverageInPercentage)
Function that combines all prior functions to one function. It generates a satellite image as a tif file. \
**parameters:** \
**bottomLeftX** (Float) \
**bottomLeftY** (Float) \
**topRightX** (Float) \
**topRightY** (Float) \
**datetime** (String): (example: "2021-06-01/2021-06-30") \
**resolution** in meters (Integer): (options: 10/20/60/100/200/400) \
**limit** (Integer) -> maximum count of found images from stac to be used \
**desiredBands** (vector of Strings): c("B01", "B02", "B03", "SCL") (SCL-BAND MUST BE INCLUDED) \
**cloudCoverageInPercentage** (Float) \
**returns:** see return codes
```{r generateSatelliteImageFromAOI}
generateSatelliteImageFromAOI <- function(bottomLeftX,bottomLeftY,topRightX,topRightY,datetime,limit,desiredBands,resolution,cloudCoverageInPercentage) {
  # Create bbox of coordinates
  bboxWGS84 <- getBBoxFromAOI(bottomLeftX,bottomLeftY,topRightX,topRightY)
  # Transform bbox CRS to the same CRS we use to create the cube view, so that every geometry alligns to each other
  bboxUTM <- transformBBOXcrsToUTM(bboxWGS84)
  # Querying images with rstac
  items = stacRequest(bboxUTM, datetime, limit)
  if (length(items$features) == 0) {
    return(1)
  }
  # print(items)
  # Creating an image collection
  imageCollection =  createImageCollection(desiredBands, cloudCoverageInPercentage, items)
  if (is.numeric(imageCollection)) {
    return(3)
  }
  # print(imageCollection)
  # Creating the cube view
  cubeView = createCubeView(bboxUTM, resolution, datetime)
  # print(cubeView)
  # Parallel computing
  gdalcubes_options(threads = 16)
  # Create tif file
  createTifFileFromAOI(imageCollection, cubeView)
  return(0)
}
```
### plotTifFile(filePath)
Function that loads and plots a tif file depending on a file path. \
**parameters:** \
**filePath:** path to the stored tif \
**return:** (void)
```{r plotTifFile}
plotTifFile <- function(filePath){
  library(raster)
  sentinel <- stack(filePath)
  sentinel
  plotRGB(sentinel, r=3, g=2, b=1, stretch = "lin")
}
```
## Return Codes
The main functions returns codes, which indicates if the creatiion of a TIF file was successful or not. If it was not successful the code indicates why the program failed. \
**0** - TIF file was successful created \
**1** - For the given date period and area where no items found \
**2** - Unexpected rrror \
**3** - After filtering the results from the stac_request by the cloud coverage no images were left \
